Democracy, Public Support, and Measurement Uncertainty

### 2021-06-29 paper/dcpo_demsupport.Rmd
Clean the scripts for everything except for moc

# load all the packages you will use below 
p_load(
  # data scrapping
  dataverse, 
  osfr,
  # DCPOtools, 
  mitools,
  boot, 
  here,
  # analysis
  plm, 
  rstan, 
  # presentation
  flextable, 
  broomExtra, 
  kableExtra, 
  modelsummary, 
  gridExtra,
  latex2exp,
  drhutools,
  dotwhisker, 
  # data wrangling
  tidyverse, 
  janitor, 
  glue, 
  qs
)

@@

@@

```{r compare_n, eval = TRUE}
dcpo_input_raw1 <-
    read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>%
    filter(!(
        str_detect(survey, "army_wvs") &
            # WVS obs identified as problematic by Claassen
            ((country == "Albania" & year == 1998) |
                 (country == "Indonesia" &
                      (year == 2001 | year == 2006)) |
                 (country == "Iran" & year == 2000) |
                 (country == "Pakistan" &
                      (year == 1997 | year == 2001)) | # 1996 in Claassen
                 (country == "Vietnam" & year == 2001)
            ) |
            (str_detect(item, "strong_wvs") &
                 ((country == "Egypt" & year == 2012) |
                      (country == "Iran" &
                           (year == 2000 | year == 2007)) | # 2005 in Claassen
                      (country == "India") |
                      (country == "Pakistan" &
                           (year == 1997 | year == 2001)) | # 1996 in Claassen
                      (country == "Kyrgyzstan" &
                           (year == 2003 | year == 2011)) |
                      (country == "Romania" &
                           (year == 1998 | year == 2005 | year == 2012)) |
                      (country == "Vietnam" & year == 2001)
                 )) |
            (
                country %in% c(
                    "Puerto Rico",
                    "Northern Ireland",
                    "SrpSka Republic",
                    "Hong Kong SAR China"
                )
            )
    )) %>%
    with_min_yrs(2)

@@

```{r pointAJPS}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

result_cls <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
names(result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
})

@@

  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
})

@@

result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))

@@

result_ajpsPooled <-
  list(result_cls,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$pooled[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_ajpsRegime <-
  list(result_cls,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

@@

```{r pointAPSR}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
})

@@

```{r num-pointAJPS, results='asis'}
tb_result_cls <- map(result_cls, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

# Results Accounting for the Uncertainty in Both the Outcome and Explanatory Variables

```{r cls-uncertainAJPSmain, eval=FALSE}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

sd_control <- sd.plm %>%
  mutate(
    country = as.character(Country),
    year = as.numeric(as.character(Year)),
    regime = ifelse(Regime_VD > 1, 1, 0)
  )

df_cls <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(sd_control, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_clsUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
})

names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```

```{r dcpo-uncertainAJPSmain, eval=FALSE}
# df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
#  .x[[.y]] %>%
#    mutate(theta_dem = theta * regime,
#           theta_aut = theta * (1 - regime)) %>%
#    plm::pdata.frame(index = c("country", "year"))
# }) # The code is to fit the embedded format of dcpo_ajps_rubin

# df_dcpo <- purrr::map(1:1000, function(anEntry) {
#   dcpo_theta$theta[anEntry,,] %>% 
#     reformat_dcpo_output("theta") %>% 
#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
#               by = c("year", "country")) %>%
#     left_join(df_controls, by = c("country", "year")) %>% 
#     mutate(theta_dem = theta * regime,
#            theta_aut = theta * (1 - regime)) %>% 
#     plm::pdata.frame(index = c("country", "year"))
# })

result_dcpoUncertain <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  mod_eval <- function(aData) eval(parse(text = aMod))

  result <- map(df_dcpo, mod_eval)

  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
})

names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```

```{r cls-undertainAPSRmain, eval=FALSE}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

sd_control <- sd.plm %>%
  mutate(
    country = as.character(Country),
    year = as.numeric(as.character(Year))
  )

df_clsAPSR <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    # left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
    #           by = c("year", "country")) %>%
    left_join(sd_control, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_clsUncertainAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
})

names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))

```{r dcpo-uncertainAPSRmain, eval=FALSE}
result_expAPSR <- map(ls_mod_apsrDCPO, function(aMod){ # reading a model
  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

saveRDS(result_expAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
```

# Replications of Full Pack of Models in Claassen 2020a,b

```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10, eval=TRUE}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
# What I've tried
# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
# 2. redefining the order of model in the dataframe or in dwplot 
# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
# 4. Every post online is to reverse

# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS

result_regime <- bind_rows(
  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n demo only\n (t-1)",
      "Support\n auto only\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))

plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
    scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

legend <- get_legend(plot_AJPS2)

plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")

grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7, eval=TRUE}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_pureAJPS$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAJPS$pooled[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
  mutate(result_pureAJPS$gmm[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAJPS$gmm[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
# What I've tried
# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
# 2. redefining the order of model in the dataframe or in dwplot 
# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
# 4. Every post online is to reverse

# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS

result_regime <- bind_rows(
  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_pureAJPS$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAJPS$`pooled-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_pureAJPS$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAJPS$`gmm-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n demo only\n (t-1)",
      "Support\n auto only\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))

plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
    scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

legend <- get_legend(plot_AJPS2)

plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")

grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", fig.width=7.5, fig.height=10, eval=TRUE}

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

# Regime compacted ####

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$pooled1[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$fd1[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms1 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]")))

plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Public Support for Democracy",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$pooled2[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$fd2[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms2 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]",
                      "Delta~Corruption",
                      "Corruption[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]",
                               "Delta~Corruption",
                               "Corruption[t-1]")))

plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

# Regime specified ####

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$`pooled-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$`fd-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms3 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")))

plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$`pooled-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_expAPSR$`fd-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms4 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP",
                      "Log~GDP[t-1]",
                      "Delta~Corruption",
                      "Corruption[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Electoral~democracy",
                               "Electoral~democracy[t-1]",
                               "Delta~Minoritarian~democracy",
                               "Minoritarian~democracy[t-1]",
                               "Delta~Log~GDP",
                               "Log~GDP[t-1]",
                               "Delta~Corruption",
                               "Corruption[t-1]")))

>>>>

# load all the packages you will use below 
p_load(
  # data scrapping
  dataverse, 
  osfr,
  DCPOtools,
  mitools,
  boot, 
  here,
  # analysis
  plm, 
  rstan, 
  # presentation
  flextable, 
  broomExtra, 
  kableExtra, 
  modelsummary, 
  gridExtra,
  latex2exp,
  drhutools,
  dotwhisker, 
  # data wrangling
  tidyverse, 
  janitor, 
  glue, 
  qs
)

@@

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

@@

```{r compare_n, eval = TRUE}
dcpo_input_raw1 <-
    read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>%
    filter(!(
        str_detect(survey, "army_wvs") &
            # WVS obs identified as problematic by Claassen
            ((country == "Albania" & year == 1998) |
                 (country == "Indonesia" &
                      (year == 2001 | year == 2006)) |
                 (country == "Iran" & year == 2000) |
                 (country == "Pakistan" &
                      (year == 1997 | year == 2001)) | # 1996 in Claassen
                 (country == "Vietnam" & year == 2001)
            ) |
            (str_detect(item, "strong_wvs") &
                 ((country == "Egypt" & year == 2012) |
                      (country == "Iran" &
                           (year == 2000 | year == 2007)) | # 2005 in Claassen
                      (country == "India") |
                      (country == "Pakistan" &
                           (year == 1997 | year == 2001)) | # 1996 in Claassen
                      (country == "Kyrgyzstan" &
                           (year == 2003 | year == 2011)) |
                      (country == "Romania" &
                           (year == 1998 | year == 2005 | year == 2012)) |
                      (country == "Vietnam" & year == 2001)
                 )) |
            (
                country %in% c(
                    "Puerto Rico",
                    "Northern Ireland",
                    "SrpSka Republic",
                    "Hong Kong SAR China"
                )
            )
    )) %>%
    DCPOtools::with_min_yrs(2)

@@

```{r pointAJPS, eval=TRUE}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

result_clsAJPS <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
names(result_clsAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_clsAJPS, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

  result_apsrAJPS <- list(tidy_clsUncertain, glance_clsUncertain)
})

@@

  result_expAJPS <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
})

@@

@@

result_ajpsPooled <-
  list(result_clsAJPS,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$pooled[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_ajpsRegime <-
  list(result_clsAJPS,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

@@

```{r pointAPSR, eval=TRUE}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

  result_apsrAJPSAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
})

@@

```{r num-pointAJPS, results='asis'}
tb_result_cls <- map(result_clsAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

# Replication with Alternative Methods Accounting for Uncertainty
```{r MocclaassenUncertaintyAJPS}
load(here("data","cls_ajps.rda"))

df_cls <- purrr::map(1:900, function(anEntry) {
  cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})
